An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-28 draft.tex
Resolving comments

@@

Having a multi-population based algorithm can decrease the execution time
because of the parallel execution of the evolution. But, having heterogeneous
populations might enhance evolutionary search and need less
evaluations than homogeneous systems; heterogeneous settings, if
done right, will increase the diversity of the whole population % cita
                                % multikulti o similar - JJ

% Explain that heterogeneity comes from using different algorithms,
% not from using different types of nodes - JJ
But this is a rule of thumb, and it will depend on the degree of
heterogeneity, as well as on the algorithm itself. In this experiment, we compare the performance of both heterogeneous and
homogeneous settings. We compare a multi-population with only  GA and PSO
populations, versus an ensemble of GA and PSO algorithms on the first five
functions of the BBOB testbed.  We used ten populations and 8 workers for the
experiment and the same parameters as before.

@@

@@

>>>>

%

@@

Having a multi-population based algorithm can decrease the execution time
because of the parallel execution of the evolution. But, having heterogeneous 
populations might enhance evolutionary search and needless
evaluations than homogeneous systems; heterogeneous settings, if
done right, increases the diversity of the whole population \cite{araujo2008multikulti}. % cita
                                % multikulti o similar - JJ

% Explain that heterogeneity comes from using different algorithms,
% not from using different types of nodes - JJ 
% done - Mario 
But this is a rule of thumb, and it will depend on the degree of heterogeneity,
as well as on the algorithm itself. Some level of heterogeneity can be
implemented by just changing the configuration parameters of each population,
but in this case, we are interested in a heterogeneous search strategy. 
Therefore, in this experiment we compare a multi-population with only GA and PSO populations,
versus an ensemble of GA and PSO algorithms. We tested on the first five functions of the
BOBB testbed. We used ten populations and 8 workers for the experiment and the
same parameters as before.

\subsection{Hardware}
\label{sec:hardware}

@@

We present the results of the experiments in this section. The effect of a
different number of populations on execution time is reported in  Section
\ref{sec:exp1results}. The results of the performance comparison between homogeneous and
heterogeneous search strategies are presented in   Section \ref{sec:exp2results}.

\subsection{Experiment 1}
\label{sec:exp1results}

@@

\subsection{Experiment 2}
\label{sec:exp2results}
